\myTitle

### 2024-11-07 tex/body-text-of-paper.tex

As sequencing costs drop, whole genome sequence (WGS) data may become the preferred
data type for salmon genetics. If so, it may become possible to include
all the >200 genetically distinct Chinook salmon populations in North America within a
single standardized reference baseline
constructed with WGS data
that performs equally well at broad and regional scales \citep{desaixINPRESSpopulation}.
Such an approach would be highly flexible and extensible, as it would allow for the use of
just about any marker type, including reduced representation DNA sequencing
\citep[e.g.,~RADseq,][]{meek2020identifying,thompson2024genomics},
as regional monitoring datasets would not need to be replicable.  For the present, however,
baselines tailored to specific regions are essential for regional management questions and
targeted sequencing approaches have proven to be the most practical for large-scale
applications of either GSI, PBT or an integrated monitoring program \citep{beacham2021parentage}.

@@

>>>>

@@

As sequencing costs drop, whole genome sequence (WGS) data may become the preferred
data type for salmon genetics. If so, it may become possible to include
all the >200 genetically distinct Chinook salmon populations in North America within a
single standardized reference baseline constructed with WGS data
that performs equally well at broad and regional scales \citep{desaixINPRESSpopulation}.
Such an approach would be highly flexible and extensible, as it would allow for the 
assignment of unknown-origin fish using
just about any marker type, including reduced representation DNA sequencing
\citep[e.g.,~RADseq,][]{meek2020identifying,thompson2024genomics},
as the variation used by such region-specific panels of markers should be contained within the WGS baseline dataset.
For the present, however,
baselines tailored to specific regions are essential for regional management questions and
targeted sequencing approaches have proven to be the most practical for large-scale
applications of either GSI, PBT or an integrated monitoring program \citep{beacham2021parentage}.

\section*{Acknowledgements}
Many people from various agencies and watershed groups contributed to the collection
of the samples analyzed here, including staff from the California Department of Fish and Wildlife,
National Marine Fisheries Service, US Fish and Wildlife Service, US Army Corps of Engineers and 
Pacific States Marine Fisheries Commission. We also thank Elena Correa, Nicole Anderson and Libby
Gilbert-Horvath for contributions to data collection. The manuscript was improved by comments from
Jeff Rodzen.
